Report for Qualifying Exam

### 2024-08-11 src/sections/introduction.tex
changed title, modified RP1

\section{Introduction} \label{sec:introduction}
In the digital age, online information seekers frequently encounter \emph{search results} laden with \emph{misinformation}, \emph{biased narratives}, and \emph{conspiracy theories}.
This exposure can potentially lead users to accept and propagate false information.
However, this phenomenon is not universal across all search queries.
Certain searches, known as \textit{data voids} are particularly susceptible to these issues.
\\
\textit{Data voids} occur when searching for terms that yield limited, non-existent, or highly problematic relevant information.
Unlike common searches that produce abundant data, queries falling into data voids may return no results or present irrelevant and often inaccurate information.
Data voids can be mainly categorized into two main types:
\begin{itemize}
    \item newly coined terms with no established information base, and
    \item existing terms whose meanings have evolved over time.
\end{itemize}
This report focuses on the latter, examining data voids where context drift occurs.
The following papers has been selected to explore this phenomenon.
\begin{itemize}
    \item Statistically Significant Detection of Linguistic Change.
    ACM WWW 2014 ~\cite{kulkarni2014statisticallysignificantdetectionlinguistic}
    \item Diachronic Word Embeddings Reveal Statistical Laws of Semantic Change.
    ACL 2016 ~\cite{hamilton-etal-2016-diachronic}
\end{itemize}

\subsection{What is a Data Void?}\label{subsec:what-is-a-data-void?}
Data voids, as first introduced by Golebiewski and Boyd \cite{unknown},
are identified while searching terms for which relevant information is either limited, non-existent, or deeply problematic.
\\
For example, unlike a typical web search for `basketball' that yields a vast amount of data,
data voids present a problematic scenario such as searches on these terms may return no results or irrelevant, often inaccurate information.
This situation could prompt users to pursue information, click on misleading search outcomes, and be exposed to false or misleading content,
ultimately shaping their perceptions and beliefs with misinformation.

Data Voids often originate in fringe communities.
When vulnerable users search for information using this term, they may encounter results that are misrepresentations of the topic, as these fringe communities have already shaped the narrative.
Mainstream media, particularly those with far-left or far-right biases, may pick up and amplify these narratives, contributing to the misinformation cycle.

\subsection{Example of a data void?(Migrant Caravan)}
Let's understand data void through an example of a term - \emph{migrant caravan}
The term ‘migrant caravan’ originally described a group of migrants traveling together for safety and mutual support.
However, its usage, particularly in political discussions, has taken on a more negative tone.
Today, it is commonly associated with large groups of migrants, often from Central America, journeying through Mexico to reach the United States.

\subsection{Lifecycle of data void (from long tail to spike)}
\subsection{Types of Data Void}
\subsection{Technical Challenge}
analyzing data void involves context drift over historical time. (How context drift happens with data void.)

>>>>

\section{Introduction} \label{sec:introduction}
Language is a dynamic, living entity that continually adapts to reflect the changing world around us.
With the evolving language, words take on new meanings through technological advancements, cultural shifts, and political movements.

Particularly in political contexts, certain words or phrases can experience rapid shifts in meaning or become ambiguous.
These are known as `data voids' - situations where the meaning of a term has become unstable or contested, often due to deliberate efforts by political actors to redefine it.

Unlike more general language evolution, where new terms emerge to describe novel concepts, data voids in politics involve the strategic manipulation of existing vocabulary.
Political actors may repurpose words or introduce new phrases to frame debates in their favor, creating confusion and a lack of shared understanding.

This phenomenon highlights how language can be weaponized as a political tool.
As terms take on drastically different meanings for different groups, it can become challenging to maintain clear, authoritative information about their usage.
The resulting `data voids' can then be exploited to spread misinformation or propaganda.

My research goal is to find data voids in political context automatically and systematically study how word shifts their meaning over time.
To achieve this, we have selected following research papers as a foundation for our research.

\begin{itemize}
    \item Statistically Significant Detection of Linguistic Change.
    ACM WWW 2015 ~\cite{kulkarni2014statisticallysignificantdetectionlinguistic}
    \item Diachronic Word Embeddings Reveal Statistical Laws of Semantic Change.
    ACL 2016 ~\cite{hamilton-etal-2016-diachronic}
\end{itemize}

The concept of context drift, as presented in these papers, refers to the change in the contextual usage of words over time.
This can be particularly useful for detecting and analyzing data voids in political contexts.

Finding data voids is significantlly important because
political events or campaigns can cause sudden changes in how certain terms are used or interpreted.
Political actors may deliberately redefine terms or introduce new phrases to frame debates in their favor.
Words or phrases can take on drastically different meanings in different political contexts or for different groups.
Some terms may develop coded political meanings that aren't immediately apparent to all audiences.
The lack of clear, authoritative information about a term's new political meaning can be exploited to spread misinformation or propaganda.

These elements can rapidly change the basic meaning (denotation) and the feelings or ideas they evoke (connotation) of words, making them challenging to track and analyze.

\para{Example.}
The term \emph{crisis actor} has undergone a significant shift in meaning,
exemplifying the phenomenon of context drift we've been discussing.

Originally this term was used in the entertainment and training industries,
which refers to individuals hired to portray victims or other roles in simulated emergency scenarios.
These simulations were used for training first responders, military personnel, or for other educational purposes.

However, in recent years, the term has been full of misinformation which refers to genuine victims of violent events (mass shooting) in an attempt to prove that an event was staged or did not happen.
This term got prominent during Sandy Hook Elementary School shooting (2012), Los Angeles International Airport (LAX) shooting (2013), Pulse Nightclub shooting in Orlando (2016), Las Vegas shooting (2017).

This example clearly demonstrates how a term with a specific, legitimate meaning can be repurposed to spread misinformation and conspiracy theories.
The shift creates a potential data void where searches for \emph{crisis actor} might lead to a mix of factual information about emergency training and harmful conspiracy theories,
making it difficult for users to distinguish accurate information.

### 2024-08-11 src/sections/paper_hamilton.tex
changed title, modified RP1

\subsection{Evaluation \& Results}
They compared the different approaches discussed in \Cref{subsec:constructing-word-embeddings} on \emph{synchronic accuracy} (similarity within time-period) and \emph{diachronic validity} (semantic changes over time).
\begin{itemize}
    \item \para{Synchronic Accuracy}
    Synchronic accuracy refers to the accuracy with which word embeddings capture the semantic relationships and meanings of words at a \emph{specific point in time}.
    It assesses how well the models represent the semantic relationships among words in a given time period.
    SVD performed best here.
    \item \para{Diachronic Validity}
    Diachronic validity evaluates how effectively the methods can detect and quantify changes in \emph{meaning over time}.
    It involves testing the methods against historical data to see if they can accurately identify known shifts in word meanings.
    The results indicated that SGNS was particularly effective in capturing these shifts, followed by SVD and PPMI.
    \begin{itemize}
        \item \textbf{Detecting Known Shifts.}
        The goal in this task is for the methods to correctly capture whether pairs of words moved closer or further apart in semantic space during a pre-determined time-period.

@@

\subsection{Statistical Laws of Semantic Change}
The authors establish two statistical laws of semantic change by analyzing a large dataset across multiple languages and time periods.
They demonstrate these laws by involving the comparison of different word embedding models (PPMI, SVD, SGNS) against known historical semantic shifts and novel benchmarks.

@@

\subsection{Takeaways}
This paper explores how different types of word embedding models, such as PPMI, SVD, and SGNS, can be used to study diachronic shifts in word meanings.
By analyzing these aligned embeddings, the authors identify two key statistical laws of semantic change.
These findings provide a quantitative framework for understanding how and why languages evolve over time.

>>>>

\subsection{Evaluation \& Results}\label{subsec:evaluation&results}
They compared the different approaches discussed in \Cref{subsec:constructing-word-embeddings} on \emph{synchronic accuracy} (similarity within time-period) and \emph{diachronic validity} (semantic changes over time).
\begin{itemize}
    \item \para{Synchronic Accuracy}
    Synchronic accuracy refers to the accuracy with which word embeddings capture the semantic relationships and meanings of words at a \emph{specific point in time}.
    It assesses how well the models represent the semantic relationships among words in a given time period.
    SVD performed best here.
    \item \para{Diachronic Validity}
    Diachronic validity evaluates how effectively the methods can detect and quantify changes in \emph{meaning over time}.
    It involves testing the methods against historical data to see if they can accurately identify known shifts in word meanings.
    The results indicated that SGNS was particularly effective in capturing these shifts, followed by SVD and PPMI\@.
    \begin{itemize}
        \item \textbf{Detecting Known Shifts.}
        The goal in this task is for the methods to correctly capture whether pairs of words moved closer or further apart in semantic space during a pre-determined time-period.

@@

\subsection{Statistical Laws of Semantic Change}\label{subsec:statistical-laws-of-semantic-change}
The authors establish two statistical laws of semantic change by analyzing a large dataset across multiple languages and time periods.
They demonstrate these laws by involving the comparison of different word embedding models (PPMI, SVD, SGNS) against known historical semantic shifts and novel benchmarks.

@@

\subsection{Takeaways}\label{subsec:takeaways4}
This paper explores how different types of word embedding models, such as PPMI, SVD, and SGNS, can be used to study diachronic shifts in word meanings.
By analyzing these aligned embeddings, the authors identify two key statistical laws of semantic change.
These findings provide a quantitative framework for understanding how and why languages evolve over time.

### 2024-08-11 src/sections/paper_kulkarni.tex
changed title, modified RP1

\para{Construction of Time Series.}
In this paper, three methods are explored for statistically modeling the evolution of words over time:
frequency analysis, part-of-speech tagging, and word co-occurrence to create time series for each word.

@@

\para{Frequency-based method.}
The simplest and most direct method for detecting sudden changes in word usage is by analyzing frequency trends.
This approach examines how often a word is used over a given period, providing insights into shifts in its popularity or relevance.
Changes in frequency can indicate whether a word is gaining new meanings or losing old ones, reflecting broader cultural or societal trends.
For example, the word “gay” in \Cref{fig:example-gay} shows a noticeable spike in usage during the 1980s, signaling a shift in its meaning or cultural relevance.

@@

\subsection{Takeaways}\label{subsec:takeaways}
For the first research question, Kulkarni et al.\ (2015) explored multiple dimensions of word usage change over time.
To address this, they constructed three types of time series: frequency-based, syntactic, and distributional.
Among these, the distributional time series proved most insightful, as it captures the contextual usage of word.
This approach utilized word embeddings to capture the semantic context of a word within specific time periods.
Subsequently, these embeddings were aligned into a unified space,
and it relied on assumptions about word stability and embedding space linearity.

@@

\para{Change Point Algorithm.}
The first step is to normalize the time series data for the word $w$.
After normalization, the algorithm computes a mean shift series, denoted as $K(Z(w))$.
The mean shift is defined as the difference in the mean of a time series at different time points.
The algorithm calculates this shift by segmenting the time series around a pivot point, denoted as time point $j$, and comparing the means of the segments before and after this point.
To assess the significance of the computed mean shifts, the algorithm employs a bootstrapping method.
This involves generating multiple bootstrap samples, denoted as $BS$.
This is done by repeatedly drawing samples from the normalized data $Z(w)$ until the number of samples equals $B$, which is predefined.
For each sample, the algorithm calculates a p-value for each time point $i$.
This p-value indicates how likely it is that the observed change at that time point is significant.
The algorithm identifies potential change points by looking for times $j$ where the Z-Score $Z_j(w)$ is greater than or equal to the threshold $\gamma$.
It then checks the p-values for these change points and selects the one with the smallest p-value, indicating the most significant change.
The algorithm returns the p-value and the estimated change point (ECP).

This information helps understand exactly when the meaning or usage of the word has shifted over time.

\subsection{Takeaways}\label{subsec:takeaways2}
The algorithm (\Cref{subsec:kulkarni-rq2}) presented in the paper computes the mean shift series as part of its approach to detect significant changes in linguistic usage over time.
The paper illustrates this with the example of the word `tape,' which transitioned from meaning adhesive tape to cassette tape, with the change detected in the 1970s.
Similarly, the word `apple' shifted from being used primarily as a common noun to a proper noun associated with Apple Inc., with this change occurring around 1984.
These examples illustrate the algorithm’s capability to pinpoint when a word’s usage and meaning undergo significant shifts.
The paper emphasizes the importance of analyzing these changes to understand linguistic evolution better.

However, the effectiveness of this method can be constrained by its sensitivity to data perturbations and the quality of annotations.
The performance of the methods, particularly the Syntactic method, declines as the perturbation increases.
This indicates that while the method may work well under minimal changes, it struggles to maintain accuracy when the changes in the data are more pronounced

@@

\para{Time Series Analysis \& Historical Analysis.}
The results presented in Kulkarni et al.\ (2015) illustrate how words acquire new meanings and how these meanings change over time through time series and historical analysis.

\para{Frequency \& Distributional.}
For words like `transmitted,' `bitch,' `sex,' and `her,' the frequency and distributional methods reveal significant insights.
For example, the sharp increase in the frequency of the word `her' around the 1960s can be attributed to the concurrent rise of the feminist movement.
However, the frequency method can produce many false positives due to the temporary popularity of specific social and political events.

@@

\para{Syntactic Method.}
The syntactic method uniquely detected the word `apple,' which saw its most frequent part of speech tag shift significantly from `Noun' to `Proper Noun.'
This method has a low false positive rate but suffers from a high false negative rate, as evidenced by its detection of only two words in the study.

\para{Distributional.}
For words like `diet,' `tape,' and `plastic,' the distributional method sheds light on significant changes in their usage.
The popularity of dieting books, starting with the bestseller `Dr. Atkins’ Diet Revolution' by Robert C. Atkins in 1972, shifted the meaning of `diet' from simply referring to the food consumed to a lifestyle of food consumption behavior.

@@

\para{Cross Domain Analysis.}
The study extends its analysis to datasets like Amazon Reviews and Twitter, which cover much shorter time scales compared to the Google Books Ngram Corpus.
This cross-domain analysis explores the impact of applying the distributional method on these more temporally constrained datasets.
\Cref{tab:sources-examples} presents words that exhibit semantic change across various datasets.

>>>>

\para{Construction of time series.}
In this paper, three methods are explored for statistically modeling the evolution of words over time:
frequency analysis, part-of-speech tagging, and word co-occurrence to create time series for each word.

@@

\para{Frequency method.}
The simplest and most direct method for detecting sudden changes in word usage is by analyzing frequency trends.
This approach examines how often a word is used over a given period, providing insights into shifts in its popularity or relevance.
Changes in frequency can indicate whether a word is gaining new meanings or losing old ones, reflecting broader cultural or societal trends.
For example, the word “gay” in \Cref{fig:example-gay} shows a noticeable spike in usage during the 1980s, signaling a shift in its meaning or cultural relevance.

@@

\subsection{Takeaways}\label{subsec:takeaways}
For the first research question, Kulkarni et al.\ (2015) explored multiple dimensions of word usage change over time.
To address this, they constructed three types of time series: frequency-based, syntactic, and distributional.

Frequency-based method relies on analyzing the frequency of word usage over time.
It provides immediate insights into trends and spikes in word usage.
However, the frequency method is prone to sampling errors, it may indicate a change in frequency without a significant shift in meaning,
as seen with the word `Hurricane' during events like Hurricane Sandy, where frequency increased but meaning remained stable.
Syntactic-based method analyzes the part of speech (POS) tags of words to detect changes in their syntactic roles over time.
Distributional-based method is based on the fact that words appearing in similar contexts are semantically similar.

Among the three methods employed by Kulkarni et al.\ (2015) for constructing time series,
the distributional time series proved most insightful, as it captures the contextual usage of word.
This approach utilized word embeddings to capture the semantic context of a word within specific time periods.

The syntactic method, while reliable in detecting changes in part-of-speech tags, may overlook significant shifts due to its reliance on linguistic taggers.
At the time of the study, this posed a challenge due to the limitations of tagging accuracy, which has since improved significantly with the advent of more advanced methods for annotating datasets with POS tags.

@@

\begin{figure}[htb]
    \centering
    \vspace{-1em}
    \includegraphics[scale=0.17]{figures/changepoint}
    \vspace*{-0.5cm}
    \caption{Change Point Algorithm (taken from \cite{kulkarni2014statisticallysignificantdetectionlinguistic}).}
    \label{fig:kulkarni-changepoint}
\end{figure}

\para{Change point algorithm.}
After constructing time series data for each word in the corpus—whether using frequency-based, syntactic, or distributional methods (\Cref{subsec:constructing-word-embeddings}), the first step is to normalize the time series data for the word $w$.
After normalization, the algorithm computes a mean shift series, denoted as $K(Z(w))$.
The mean shift is defined as the difference in the mean of a time series at different time points.
The algorithm calculates this shift by segmenting the time series around a pivot point, denoted as time point $j$, and comparing the means of the segments before and after this point.
To assess the significance of the computed mean shifts, the algorithm employs a bootstrapping method.
This involves generating multiple bootstrap samples, denoted as $BS$.
This is done by repeatedly drawing samples from the normalized data $Z(w)$ until the number of samples equals $B$, which is predefined.
For each sample, the algorithm calculates a p-value for each time point $i$.
This p-value indicates how likely it is that the observed change at that time point is significant.
The algorithm identifies potential change points by looking for times $j$ where the Z-Score $Z_j(w)$ is greater than or equal to the threshold $\gamma$.
It then checks the p-values for these change points and selects the one with the smallest p-value, indicating the most significant change.
The algorithm returns the p-value and the estimated change point (ECP).
This information helps understand exactly when the meaning or usage of the word has shifted over time.
\Cref{fig:kulkarni-changepoint} illustrates the important aspects of the algorithm.

\subsection{Takeaways}\label{subsec:takeaways2}
The change point detection algorithm (\Cref{subsec:kulkarni-rq2}) presented in the paper detects significant linguistic shifts over time by analyzing word time series data.
To detect changes, they first convert these time series into Z-score series, which normalize the data and make it easier to identify shifts.
The Mean Shift model is then applied, which involves calculating the mean of the time series data before and after each potential change point.
By comparing these means, the algorithm determines if a statistically significant change has occurred at any given point in time.

The paper illustrates this with the example of the word `tape,' which transitioned from meaning adhesive tape to cassette tape, with the change detected in the \emph{1970s}.
Similarly, the word `apple' shifted from being used primarily as a common noun to a proper noun associated with Apple Inc., with this change occurring around \emph{1984}.

These examples illustrate the algorithm’s capability to pinpoint when a word’s usage and meaning undergo significant shifts.
The paper emphasizes the importance of analyzing these changes to understand linguistic evolution better.

@@

\para{Time series analysis \& historical analysis.}
The results presented in Kulkarni et al.\ (2015) illustrate how words acquire new meanings and how these meanings change over time through time series and historical analysis.

\para{Frequency method.}
For words like `transmitted,' `bitch,' `sex,' and `her,' the frequency and distributional methods reveal significant insights.
For example, the sharp increase in the frequency of the word `her' around the 1960s can be attributed to the concurrent rise of the feminist movement.
However, the frequency method can produce many false positives due to the temporary popularity of specific social and political events.

@@

\para{Syntactic method.}
The syntactic method uniquely detected the word `apple,' which saw its most frequent part of speech tag shift significantly from `Noun' to `Proper Noun.'
This method has a low false positive rate but suffers from a high false negative rate, as evidenced by its detection of only two words in the study.

\para{Distributional method.}
For words like `diet,' `tape,' and `plastic,' the distributional method sheds light on significant changes in their usage.
The popularity of dieting books, starting with the bestseller `Dr. Atkins’ Diet Revolution' by Robert C. Atkins in 1972, shifted the meaning of `diet' from simply referring to the food consumed to a lifestyle of food consumption behavior.

@@

\para{Cross domain analysis.}
The study extends its analysis to datasets like Amazon Reviews and Twitter, which cover much shorter time scales compared to the Google Books Ngram Corpus.
This cross-domain analysis explores the impact of applying the distributional method on these more temporally constrained datasets.
\Cref{tab:sources-examples} presents words that exhibit semantic change across various datasets.

### 2024-08-11 src/sections/relatedwork.tex
changed title, modified RP1

\section{Related Work} \label{sec:relatedwork}
\para{Tracking how word meanings change over time.}
The evolution of word meanings over time has been a subject of significant interest.
Researchers employed a diverse array of methodologies, including \emph{word embeddings} ~\cite{kulkarni2014statisticallysignificantdetectionlinguistic},
\emph{neural language models} ~\cite{kim-etal-2014-temporal}, and \emph{diachronic analysis} ~\cite{hamilton-etal-2016-diachronic, kutuzov-etal-2018-diachronic},
to track and examine semantic shifts across historical periods.
Much of this research utilized the \emph{Google Books Ngram corpus}
~\cite{gulordava-baroni-2011-distributional, kim-etal-2014-temporal, kulkarni2014statisticallysignificantdetectionlinguistic, 10.1007/978-3-319-50496-4_18, hamilton-etal-2016-cultural, hamilton-etal-2016-diachronic, kutuzov-etal-2018-diachronic},
a vast collection spanning from 1900 to 2009,
encompassing over 500 billion books in seven languages.
This dataset provides n-grams with corresponding yearly occurrences and frequencies.

\begin{figure}[tbh]
\vspace{-1em}
\centering
\includegraphics[scale=0.45]{figures/survey}
\caption{Timeline of models used to study semantic shifts (taken from \cite{kutuzov-etal-2018-diachronic})}\label{fig:testsvg}
\end{figure}

@@

\subsection{Takeaways}\label{subsec:semantic-takeaways}
Existing research on semantic change detection employs a diverse range of methods.
Traditional approaches rely on frequency analysis, such as log ratio computations\cite{gulordava-baroni-2011-distributional},
while more recent studies utilized distributional representations\cite{kim-etal-2014-temporal, kulkarni2014statisticallysignificantdetectionlinguistic, hamilton-etal-2016-cultural},
including word embeddings generated by techniques like SGNS, PPMI, and SVD\cite{hamilton-etal-2016-diachronic}.
Clustering algorithms like DBSCAN\cite{10.1007/978-3-319-50496-4_18} was applied to detect semantic shifts in polysemous words.
By clustering words based on their contextual similarity, they were able to identify when a word’s meaning had shifted, as changes in clusters indicated emerging or evolving senses.
BERT-based contextual embeddings\cite{giulianelli-etal-2020-analysing} measured lexical semantic change by capturing how word meanings shift subtly across different contexts.
The advent of word embeddings provided a quantitative framework for measuring semantic change,
leading to the identification of patterns like the \emph{law of conformity} and \emph{law of innovation} as proposed by Hamilton et al.\ (2016).
These methods have successfully identified semantic shifts in corpora spanning from the 19th to the 21st centuries, revealing changes in word meanings and usage.
Recent studies, such as Laurino et al.\ (2023), have begun to explore the rapid evolution of language in response to global events like the COVID-19 pandemic,
highlighting the dynamic nature of semantic change.
%Despite these advancements, challenges persist, such as the limited availability of methods for languages other than English and the requirement for large datasets.
%Developing algorithms capable of detecting semantic change in smaller corpora is an important area for future research.

>>>>

\section{Related Work} \label{sec:relatedwork}
\para{Tracking how word meanings change over time.}
The evolution of word meanings over time has been a subject of significant interest.
Researchers employed a diverse array of methodologies, including \emph{word embeddings} ~\cite{kulkarni2014statisticallysignificantdetectionlinguistic},
\emph{neural language models} ~\cite{kim-etal-2014-temporal}, and \emph{diachronic analysis} ~\cite{hamilton-etal-2016-diachronic, kutuzov-etal-2018-diachronic},
to track and examine semantic shifts across historical periods.
\Cref{fig:timeline} presents a chronological overview of models and events in this domain.
Much of this research utilized the \emph{Google Books Ngram corpus}
~\cite{gulordava-baroni-2011-distributional, kim-etal-2014-temporal, kulkarni2014statisticallysignificantdetectionlinguistic, 10.1007/978-3-319-50496-4_18, hamilton-etal-2016-cultural, hamilton-etal-2016-diachronic, kutuzov-etal-2018-diachronic},
a vast collection spanning from 1900 to 2009,
encompassing over 500 billion books in seven languages.
This dataset provides n-grams with corresponding yearly occurrences and frequencies.

\begin{figure}[tbh]
\vspace{-1em}
\centering
\includegraphics[scale=0.45]{figures/survey}
\caption{Timeline of models used to study semantic shifts (taken from \cite{kutuzov-etal-2018-diachronic})}\label{fig:timeline}
\end{figure}

@@

\subsection{Takeaways}\label{subsec:semantic-takeaways}
Existing research on semantic change detection employs a diverse range of methods.
Traditional approaches rely on frequency analysis, such as log ratio computations\cite{gulordava-baroni-2011-distributional},
while more recent studies utilized distributional representations\cite{kim-etal-2014-temporal, kulkarni2014statisticallysignificantdetectionlinguistic, hamilton-etal-2016-cultural},
including word embeddings generated by techniques like SGNS, PPMI, and SVD\cite{hamilton-etal-2016-diachronic}.
Clustering algorithm like DBSCAN\cite{10.1007/978-3-319-50496-4_18} was applied to detect semantic shifts in polysemous words.
By clustering words based on their contextual similarity, they were able to identify when a word’s meaning had shifted, as changes in clusters indicated emerging or evolving senses.
BERT-based contextual embeddings\cite{giulianelli-etal-2020-analysing} measured lexical semantic change by capturing how word meanings shift subtly across different contexts.
The advent of word embeddings provided a quantitative framework for measuring semantic change,
leading to the identification of laws like the \emph{law of conformity} and \emph{law of innovation} as proposed by Hamilton et al.\ (2016).
These methods have successfully identified semantic shifts in corpora spanning from the 19th to the 21st centuries, revealing changes in word meanings and usage.
Recent studies, such as Laurino et al.\ (2023), have begun to explore the rapid evolution of language in response to global events like the COVID-19 pandemic,
highlighting the dynamic nature of semantic change.
%Despite these advancements, challenges persist, such as the limited availability of methods for languages other than English and the requirement for large datasets.
%Developing algorithms capable of detecting semantic change in smaller corpora is an important area for future research.
